### 2014-10-15 Docs/managing_jobs/managingjobs.tex
add note about fno-tree-pre with gfortran 4.8.x

\item {\em gfortran 4.8.x}: There are no known issues with gfortran 4.8.x

>>>>

\item {\em gfortran 4.8.x}: This typically works well, but sometimes we get
an error allocating memory in {\tt cluster\_f.f90}.  The NERSC team looked
into this an determined it is a compiler bug (affecting atleast 4.8.2 and 4.8.3):
\begin{quote}
The code runs without any problem if it is compiled with {\tt -O2 -ftree-vectorize -fno-range-check} (our default) expcept that {\tt cluster\_f.f90} is compiled with {\tt -O2 -ftree-vectorize -fno-range-check -fno-tree-pre}.   The ``{\tt fno-tree-pre}'' option turns off ``{\tt ftree-pre}'' that is turned on by ``{\tt O2}''.

GCC manual says,

{\tt -ftree-pre} \\
Perform partial redundancy elimination (PRE) on trees. This flag is enabled by default at {\tt -O2} and {\tt -O3}.
\end{quote}
